\documentclass[../main.tex]{subfiles}
\begin{document}
    \section{History of Computing and Computer}
    It is very important for us to learn the history of the subject that we are
    going to learn. Learning history helps us understanding where we come from
    and why things are organized in the way we see today. Computer itself does
    not have very long history, but the history of computing can dates back to
    thousands of years ago, when human first learned writing.

    \subsection{Ancient History of Computer Science}
    The history of electrical computer (not even electronic) can date back to 1940s
    when ENIAC was first invented in MIT, but the history of programming and many
    other components of computer science date far earlier than that. In ancient
    Greece, Euclid proposed a group of axioms and theorems for some basic geometry
    and developed some strategy for solving basic geometry problems. This is one of
    the earliest use of algorithm.

    \subsection{Modern History of Computer Science}
    From 1940s to 1960s, technology did not evolve as rapidly as today. However,
    hardware had been constantly improving, but a few problems had emerged already:
    with the improvement of hardware, programming them became more and more
    challenging and difficult. This led to the ``software crisis'', which was first
    brought up in 1968.

    However, two significant events changed the entire histroy from 1970s until
    today: the birth of Unix operating system in 1969 and the C programming language.
    The Unix operating system was first implemented by Ken Thompson and Dennis
    Ritchie, who were working at the Bell Lab of AT\&T. Unix was the first operating
    system that realized multi-user, multi-programming, and file system on computer.
    The design philosophy of Unix operating system has influenced generations of
    computer scientists and operating systems. Linux, OS X, Android, and Chrome OS
    are all Unix-like systems. It is fair to say: without Unix, we would probably
    still in 1960s.

    The C programming language is another milestone in technology history. C was
    first implemented by Dennis Ritchie and Brian Kernighan. In 1972, Unix was
    rewritten in C, thus became the first operating system than can be run on
    multiple platforms. This significantly changed the world of programming and
    software engineering. From then, writing programs on computer has been
    significantly easier.

    In 1991, a Finnish college student, Linus Torvalds, published the very first
    version of Linux operating system, which later became the foundation of Chrome
    OS, Android, and many other embedded systems.

    Programs and Software
    Computer science is the study of computation and its applications. What is
    computation? What are its applications? One of the most important applications
    of computation is program. A program is a set of instructions that tells computer
    to perform some specific work.
\end{document}
